Causal Analysis Paper

### 2022-06-08 PaperAnalysis.Rmd
G-separation

###G-separation

"Once estimated, the Q-model (a linear regression of the outcome on the exposure and covariates) is used to predict counterfactual outcomes for each observation under each exposure regimen. This is accomplished by plugging $a=1$ and then subsequently $a=0$ into the regression fit to obtain a predicted outcome under these 2 settings. The counterfactual
outcome associated with exposure intervention a can be represented as $Y_a$. Because we have a dichotomous treatment setting, the counterfactual outcomes correspond to
$Y_1$ for exposed and $Y_0$ for unexposed. Generating counterfactual outcomes for each observation in under exposed and unexposed settings furnishes the investigator with a full data set that is free of confounding under causal assumptions and resolves the missing data problem described above."(@snowden2011implementation)

>>>>

###G-separation
G-separation or G computation is a method that enables the unbiased estimation of marginal causal effects by using counterfactuals. It thus responds to the rupture of two of the main assumptions discussed above: the missingness of counterfactuals on observational data (because it is impossible to observe participants under both treatment and non-treatment) and heterogeneity of effects ().

"Once estimated, the Q-model (a linear regression of the outcome on the exposure and covariates) is used to predict counterfactual outcomes for each observation under each exposure regimen. This is accomplished by plugging $a=1$ and then subsequently $a=0$ into the regression fit to obtain a predicted outcome under these 2 settings. The counterfactual
outcome associated with exposure intervention a can be represented as $Y_a$. Because we have a dichotomous treatment setting, the counterfactual outcomes correspond to
$Y_1$ for exposed and $Y_0$ for unexposed. Generating counterfactual outcomes for each observation in under exposed and unexposed settings furnishes the investigator with a full data set that is free of confounding under causal assumptions and resolves the missing data problem described above."[@snowden2011implementation]
